---
title: "Exploring Campaign Expenditures"
output: html_notebook
---

## Download, Load, and Clean Data 

These scripts download the campaign spending data and joins it with the filing 
ID data. The scripts work with the original data file which is large. If you're interested in working with smaller chunks of data, consider using [this script](https://github.com/Data4Democracy/campaign_expenditures/blob/master/write_by_year.Rmd) to clean and break the data up into separate years.

```{r set up}
#Don't forget to set your working directory.
#rm(list = ls())
```

```{r load packages}
library(tidyverse, quietly = T)
library(lubridate, quietly = T)
library(stringr, quietly = T)
```

Download the zip file if you don't already have it: 

```{r download data}
if (file.exists("data/expenditures.csv.zip") == FALSE) {
 download.file(
   "https://www.strongspace.com/shared/f5g1t7fcsb", 
   destfile = "data/expenditures.csv.zip",
   method = "curl"
   )}

unzip("data/expenditures.csv.zip", exdir = "data")
```

```{r load dataset}
# Load datasets and join

# Load main expenditures dataset
expend <- read_csv("data/expenditures.csv", col_names = c(
  "filing_id", "payee", "street", "city", "state", "date", "amount", "cat"
))

expend <- mutate(expend, just_year = year(date)) # Extract year

# Load filing ID data from data.world
ids <- read_csv("https://query.data.world/s/1siiy0oqmrxt8ec5d7jzmn7gj")

# Join
df <- left_join(expend, ids, by = "filing_id")
```

## Data Exploration 

This summarizes a year by reporting the total number of transactions and the 
total spent by each committe: 

```{r summarise by year}
# TODO Need to edit to account for "just_year" variable added in the 
# load dataset code chunk
# Function for summarizing x = chosen year
summariseYear <- function(df, chosenyear) {
    df %>%
        filter_(~just_year == chosenyear) %>%
        group_by_(~just_year, ~committee_name) %>%
        summarise_(.dots = setNames(list(~n(), ~sum(amount)), c("n", "total"))) %>%
        arrange_(~desc(total), ~desc(n))
}

# Example using 2016. This takes forever, so commenting out.
# y_16 <- summariseYear(df, "2016")
```

For example, here is a dataset summarizing 2016: 

```{r}
summariseYear(df, 2016)
```

This creates a dataset of travel related expenses in 2016: 

```{r subset 2016}
# Subset 2016 data
sixteen <- df %>%
  filter(just_year == "2016")
```

```{r travel 2016}
# Travel-related expenses in 2016
travel   <- filter(sixteen, str_detect(cat, regex("travel", ignore_case = T)))

travel
```

This script totals up the spending per year and sorts it from the highest totals 
to the lowest: 

```{r compare yearly totals}
# Which years had the most spending?
yearly <- df %>%
  mutate(year = format(date, "%Y")) %>%
  group_by(year) %>%
  summarise(n = n(), total = sum(amount)) %>%
  arrange(desc(total))

yearly
```

```{r bar plot total by year}
ggplot(data = yearly) +
    geom_bar(mapping = aes(reorder(x = year, total), y = total), stat = "identity") +
    coord_flip() +
  labs(
    title = "Total Campaign Spending by Year", 
    subtitle = "Years arranged in descending order of total spending",
    x = "Year by Total",
    y = "Total"
    )
```