---
title: "Payee Analysis"
output: html_notebook
---

_Reminder: Don't forget to set your working directory._

This script reads in the campaign spending dataset from 2016 and counts the 
ngrams found in the spending description vector. The counts are stored in the 
variable `words`. The ngram counts can be used to narrow down spending 
transactions into discreet categories.

```{r}
# Load packages
library(tidyverse)
library(tidytext)
```

```{r}
# Read 2013-2016 spending data from data.world
file_names <- c(
  "https://query.data.world/s/2qjud27woy0hnlngoqk42003k",
  "https://query.data.world/s/1z87vsse3wqzmfmkt26g1ac6f", 
  "https://query.data.world/s/6uk5f0kcoj6zdfye0o092v9n5", 
  "https://query.data.world/s/4hhflof4h6w5zsnrdgeux239z"
)

all_files <- lapply(file_names, read_csv)

# Combine datasets
spending <- bind_rows(all_files)
```

How many unique payees did each committee have?

```{r}
unique_payees <- spending %>%
  distinct(just_year, committee_name, payee) %>%
  group_by(just_year, committee_name) %>%
  summarise(n = n())
```

How much money did each payee receive in 2016?

```{r}
dollars_recd <- spending %>%
  group_by(just_year, payee) %>%
  summarise(total_recd = sum(amount), n = n())
```